They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-16 paper/paper.Rmd
tables 5 and 6, capital Ps

Studying both player streaks and team streaks in basketball, in both observational and controlled settings. Gilovich et al. [-@gilovich1985] do not find evidence for the hot hand phenomenon. However, Miller and Sanjurjo [-@miller2018] refuted the conclusions of Gilovich et al., proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy. Specifically, Miller and Sanjurjo say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d. conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success". When applying streak selection bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite conclusions as Giloveih et al.

Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports. Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD. However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^9]

[^9]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).

@@

The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^10] winning each round is

[^10]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).

@@

```{r}
#| label: cod_series_outcome_prop-table
cod_streaks_naive_res$series |>
  select(
    n_rounds,
    prop_expected,
    prop_actual,
    n_actual
  ) |>
  arrange(n_rounds) |>
  gt::gt() |>
  gt::cols_label(
    n_rounds = 'Series lasts\nr rounds',
    prop_expected = 'P_{E}(r)',
    prop_actual = 'P_{O}(r)',
    n_actual = 'N_O'
  ) |>
  gt::fmt_percent(
    decimals = 1,
    columns = c('prop_expected', 'prop_actual')
  ) |>
  gt::tab_spanner(
    label = 'Observed',
    columns = c('prop_actual', 'n_actual')
  ) |>
  gt::as_latex()
```

@@

```{=tex}
\begin{longtable}{rrrr}
\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game. The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
\toprule
&  & \multicolumn{2}{c}{Observed} \\ 
\cmidrule(lr){3-4}
Series lasts $r$ rounds & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
\midrule
6 & $3.1\%$ & $4.7\%$ & 40 \\ 
7 & $9.4\%$ & $11.9\%$ & 101 \\ 
8 & $16.4\%$ & $16.5\%$ & 141 \\ 
9 & $21.9\%$ & $21.7\%$ & 185 \\ 
10 & $24.6\%$ & $21.5\%$ & 183 \\ 
11 & $24.6\%$ & $23.7\%$ & 202 \\ 
\bottomrule
\end{longtable}
```
```{r}
#| label: cod_series_outcomes_naive_chi
generate_chi_label <- function(statistic, p.value) {
  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
}

@@

cod_streaks_other_res |>
  filter(idx %in% c(0L, 2L)) |> 
  mutate(
    lab = sprintf('$p$ = %s', p)
  ) |>
  select(lab, series_streaks) |>
  unnest(series_streaks) |>
  select(lab, n_rounds, prop_expected) |>
  mutate(
    across(prop_expected, ~scales::percent(.x, accuracy = 0.1))
  ) |>
  pivot_wider(
    names_from = lab,
    values_from = prop_expected
  ) |>
  inner_join(
    cod_streaks_naive_res$series |>
      transmute(n_rounds, `$P_O(r)$` = scales::percent(prop_actual, accuracy = 0.1)),
    by = 'n_rounds'
  ) |>
  arrange(n_rounds) |>
  rename(`Series lasts $r$ rounds` = n_rounds) |>
  knitr::kable()
```

@@

```{=tex}
\begin{longtable}[]{@{}lrr@{}}
\caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
\toprule()
Method & \(p(r)\) & \(\chi^2\) (p-value) \\
\midrule()
\endfirsthead
\toprule()
Method & \(p(r)\) & \(\chi^2\) (p-value) \\
\midrule()
\endhead
0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
\bottomrule()
\end{longtable}
```
Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^11] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$. $p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.

[^11]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.

```{=tex}
\begin{longtable}[]{@{}rrrr@{}}
\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
\toprule()
Series lasts \(r\) rounds & \(p_0(r)\) = 0.5 & \(p_2(r)\) = 0.575 & \(P_O(r)\) \\
\midrule()
\endhead
6 & 3.1\% & 4.2\% & 4.7\% \\
7 & 9.4\% & 11.2\% & 11.9\% \\
8 & 16.4\% & 17.8\% & 16.5\% \\
9 & 21.9\% & 21.8\% & 21.7\% \\
10 & 24.6\% & 23.0\% & 21.5\% \\
11 & 24.6\% & 22.0\% & 23.7\% \\
\bottomrule()
\end{longtable}
```
It is fair to conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $p$ ($\approx 0.575$).

@@

```{r}
#| label: cod_round_win_prop_after_k_wins-table
cod_round_win_prop_after_k_wins |> 
  mutate(
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  filter(win_streak == 3) |> 
  arrange(win_streak, n_rounds, win_series) |> 
  transmute(
    # win_streak,
    n_rounds,
    across(win_series, ~ifelse(.x, 'win', 'lose')),
    total,
    prop,
    prior_p,
    expected_poststreak_p,
    gt_p_value,
    gt_p_value_adj
  ) |> 
  gt::gt() |> 
  gt::fmt_percent(
    decimals = 0,
    columns = c(prop, prior_p, expected_poststreak_p)
  ) |> 
  gt::cols_label(
    # win_streak = 'Streak',
    win_series = 'Win Series?',
    n_rounds = 'Series lasts r rounds',
    total = 'N',
    prop = 'O',
    prior_p = 'a',
    expected_poststreak_p = 'b',
    gt_p_value = 'a',
    gt_p_value_adj = 'b'
  ) |> 
  gt::tab_spanner(
    label = 'x',
    columns = c(prop, prior_p, expected_poststreak_p)
  ) |> 
  gt::tab_spanner(
    label = 'y',
    columns = c(gt_p_value, gt_p_value_adj)
  ) |> 
  gt::tab_footnote(
    footnote = 'Binom',
    locations = gt::cells_column_labels(columns = c(gt_p_value))
  ) |> 
  gt::as_latex()
```

@@

```{=tex}
\begin{equation}\protect\hypertarget{eq:pwkr}{}{
  \hat{p}^{kr,\text{win}}_E = \hat{p}(\text{win round | k-round winning streak, series lasting r rounds})=\{
    \begin{array}{cl}
    \frac{6 - k}{i - k}, & \text{team wins series} \\
    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
    \end{array}.
  }\label{eq:pwkr}
\end{equation}
```
$\hat{p}^{kr,loss}_E = \hat{p}(\text{lose round | k-round losing streak, series lasting r rounds})$ can be formulated symmetrically.

While one might think that $E[\hat{p}^{kr,\text{win}} - \hat{p}^{kr,\text{loss}}] = 0$, Miller and Sanjurjo [-@miller2018] suggest that, given a deterministic i.i.d. Bernoulli probability (Equation \ref{pwkr}, this is not true due to streak-selection bias.[^12][^13]

[^12]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.

[^13]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.

I apply their formulation for "downward bias" to post-streak success to come up with estimates $\hat{P}_{kr,\text{win}}^{\text{adj.}}$, specifying $r$ as the number of trials.

Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{kr,\text{win}}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series. (Some combinations of $r$ and $\text{team loses series}$ are irrelevant, such as the case when $r \in [7, 8, 9]$, so these combinations are excluded.)

@@

```{=tex}
\begin{longtable}{rrrrrrrr}
\toprule
&  &  & \multicolumn{3}{c}{$\hat{p}^{kr,\text{win}}$} & \multicolumn{2}{c}{$p$-value} \\
\cmidrule(lr){4-6} \cmidrule(lr){7-8}
Series lasts $r$ rounds & Win Series? & $N^{kr,\text{win}}_O$ & $O$ & $E$ & $\text{adj.}$ & $E$ & $\text{adj.}$ \\ 
\midrule
7 & win & 209 & $75\%$ & $75\%$ & $61\%$ & 0.58 & <=0.01 \\ 
8 & win & 209 & $62\%$ & $60\%$ & $45\%$ & 0.28 & <=0.01 \\ 
9 & win & 193 & $52\%$ & $50\%$ & $35\%$ & 0.33 & <=0.01 \\ 
10 & lose & 60 & $13\%$ & $14\%$ & $10\%$ & 0.64 & 0.26 \\ 
10 & win & 151 & $44\%$ & $43\%$ & $29\%$ & 0.45 & <=0.01 \\ 
11 & lose & 129 & $24\%$ & $25\%$ & $16\%$ & 0.63 & <=0.01 \\ 
11 & win & 150 & $40\%$ & $38\%$ & $25\%$ & 0.29 & <=0.01 \\ 
\bottomrule
\end{longtable}
```
# References {.unnumbered}

>>>>

Studying both player streaks and team streaks in basketball, in both observational and controlled settings. Gilovich et al. [-@gilovich1985] do not find evidence for the hot hand phenomenon. However, Miller and Sanjurjo [-@miller2018] refuted the conclusions of Gilovich et al., proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^9]. Specifically, Miller and Sanjurjo say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d. conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success". When applying streak selection bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite conclusions as Giloveih et al.

[^9]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect... provides a novel structural candidate explanationfor the persistence of gambler's fallacy beliefs", per Miller and Sanjurjo [-@miller2018].

Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports. Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD. However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^10]

[^10]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).

@@

The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is

[^11]: If $p > 0.5$, then one might say that this team is the better team (known in hindsight).

@@

```{r}
#| label: cod_series_outcome_prop-table
cod_streaks_naive_res$series |>
  select(
    n_rounds,
    prop_expected,
    prop_actual,
    n_actual
  ) |>
  arrange(n_rounds) |>
  gt::gt() |>
  gt::cols_label(
    n_rounds = 'r',
    prop_expected = 'P_{E}(r)',
    prop_actual = 'P_{O}(r)',
    n_actual = 'N_O'
  ) |>
  gt::fmt_percent(
    decimals = 1,
    columns = c('prop_expected', 'prop_actual')
  ) |>
  gt::tab_spanner(
    label = 'Observed',
    columns = c('prop_actual', 'n_actual')
  ) |>
  gt::as_latex()
```

@@

```{=tex}
\begin{longtable}{rrrr}
\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game. The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
\toprule
&  & \multicolumn{2}{c}{Observed} \\ 
\cmidrule(lr){3-4}
$r$ & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
\midrule
6 & $3.1\%$ & $4.7\%$ & 40 \\ 
7 & $9.4\%$ & $11.9\%$ & 101 \\ 
8 & $16.4\%$ & $16.5\%$ & 141 \\ 
9 & $21.9\%$ & $21.7\%$ & 185 \\ 
10 & $24.6\%$ & $21.5\%$ & 183 \\ 
11 & $24.6\%$ & $23.7\%$ & 202 \\ 
\bottomrule
\end{longtable}
```
```{r}
#| label: cod_series_outcomes_naive_chi
generate_chi_label <- function(statistic, p.value) {
  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
}

@@

cod_streaks_other_res |>
  filter(idx %in% c(0L, 2L)) |> 
  mutate(
    lab = sprintf('$p$ = %s', p)
  ) |>
  select(lab, series_streaks) |>
  unnest(series_streaks) |>
  select(lab, n_rounds, prop_expected) |>
  mutate(
    across(prop_expected, ~scales::percent(.x, accuracy = 0.1))
  ) |>
  pivot_wider(
    names_from = lab,
    values_from = prop_expected
  ) |>
  inner_join(
    cod_streaks_naive_res$series |>
      transmute(n_rounds, `$P_O(r)$` = scales::percent(prop_actual, accuracy = 0.1)),
    by = 'n_rounds'
  ) |>
  arrange(n_rounds) |>
  rename(`$r$` = n_rounds) |>
  knitr::kable()
```

@@

```{=tex}
\begin{longtable}[]{@{}lrr@{}}
\caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
\toprule()
Method & \(p(r)\) & \(\chi^2\) (p-value) \\
\midrule()
\endfirsthead
\toprule()
Method & \(p(r)\) & \(\chi^2\) (p-value) \\
\midrule()
\endhead
0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
\bottomrule()
\end{longtable}
```
Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$. $p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.

[^12]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$).

```{=tex}
\begin{longtable}[]{@{}rrrr@{}}
\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
\toprule()
$r$ & $p_0(r)$ = 0.5 & $p_2(r)$ = 0.575 & $P_O(r)$ \\
\midrule()
\endhead
6 & 3.1\% & 4.2\% & 4.7\% \\
7 & 9.4\% & 11.2\% & 11.9\% \\
8 & 16.4\% & 17.8\% & 16.5\% \\
9 & 21.9\% & 21.8\% & 21.7\% \\
10 & 24.6\% & 23.0\% & 21.5\% \\
11 & 24.6\% & 22.0\% & 23.7\% \\
\bottomrule()
\end{longtable}
```
It is fair to conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $p$ ($\approx 0.575$).

@@

```{r}
#| label: cod_round_win_prop_after_k_wins-table
cod_round_win_prop_after_k_wins |> 
  mutate(
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  filter(win_streak == 3, !win_series) |> 
  arrange(win_streak, n_rounds, win_series) |> 
  transmute(
    # win_streak,
    n_rounds,
    # across(win_series, ~ifelse(.x, 'win', 'lose')),
    total,
    prop,
    prior_p,
    expected_poststreak_p,
    gt_p_value,
    gt_p_value_adj
  ) |> 
  gt::gt() |> 
  gt::fmt_percent(
    decimals = 0,
    columns = c(prop, prior_p, expected_poststreak_p)
  ) |> 
  gt::cols_label(
    # win_streak = 'Streak',
    n_rounds = 'r',
    total = 'N',
    prop = 'O',
    prior_p = 'a',
    expected_poststreak_p = 'b',
    gt_p_value = 'c',
    gt_p_value_adj = 'd'
  ) |> 
  gt::tab_spanner(
    label = 'x',
    columns = c(prior_p, gt_p_value)
  ) |> 
  gt::tab_spanner(
    label = 'y',
    columns = c(expected_poststreak_p, gt_p_value_adj)
  ) |> 
  gt::as_latex()
```

@@

```{=tex}
\begin{equation}\protect\hypertarget{eq:pwkr}{}{
  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}(\text{win round | k-round winning streak, series lasting r rounds})=\{
    \begin{array}{cl}
    \frac{6 - k}{i - k}, & \text{team wins series} \\
    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
    \end{array}.
  }\label{eq:pwkr}
\end{equation}
```
$\hat{P}^{kr,loss}_{E,\text{unadj.}} = \hat{P}(\text{lose round | k-round losing streak, series lasting r rounds})$ can be formulated symmetrically.

While one might think that $E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0$, Miller and Sanjurjo [-@miller2018] suggest that, given a deterministic i.i.d. Bernoulli probability (Equation \ref{eq:pwkr}, this is not true due to streak-selection bias.[^13] As proved by Miller and Sanjurjo, TODO: Combine these two sentences

[^13]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.

> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*. Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*. In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$

TODO: Descripe the Appendix E.1. I apply their formulation for "downward bias" to post-streak success to come up with estimates $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$, specifying $r$ as the number of trials.

Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} and table \ref{tbl:cod-round-loss-prop-after-k-losses} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.

@@

TODO: Put p-value in parentheses

```{=tex}
\begin{longtable}{rrrrrrr}
\caption{Observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round-win streak, for a series lasting $r$ rounds.}\label{tbl:cod-round-win-prop-after-k-wins} \\
\toprule
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
\bottomrule
\end{longtable}
```
```{=tex}
\begin{longtable}{rrrrrrr}
\caption{Observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round-loss streak, for a series lasting $r$ rounds. $r \in [7, 8, 9]$ are invalid.}\label{tbl:cod-round-loss-prop-after-k-losses} \\
\toprule
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
\bottomrule
\end{longtable}
```
# References {.unnumbered}
